Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-06-18 paper.tex
changes to section 4

One may also notice that such a paradigm, {\it i.e.}, verification and synthesis based on an expected system behavior, is not restricted to digital filters and controllers or DMA races, but it can also be applied to possibly any real system, as long as the desired behavior can be expressed as properties in BMC frameworks. For instance, regarding self-driving cars, an important property could be the detection of pedestrians, animals, bicycles, or any obstacle present on urban and rural roads. Indeed, for instance, bicycles are considered one of the most difficult problems, due to the myriad of possible shape and colors \cite{selfcar}. In addition, the mentioned problem is closely related to machine learning, from which refinement strategies can be devised and incorporated to BMC approaches\cite{BMCml}.

@@

Generally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation~\cite{Behrend15,Lettnin09}, as shown in Figure~\ref{verification-methodologies}. 
%
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.35]{figure4.eps}
	\caption{Verification methodologies for embedded systems.}
	\label{verification-methodologies}
\end{figure}

In particular, the main challenges regarding verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, providing completeness, {\it i.e.},  if all possible states can be reached and evaluated, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness. Additionally, embedded system verification raises additional challenges, such as 
%
\begin{enumerate}
	\item time and energy constraints.
	\item handling of concurrent software.
	\item platform restrictions.
	\item verification of code pieces or modules that rely on larger structures.
	\item legacy designs. %, which are usually developed with low-level languages.
	\item support to different programming languages, frameworks, and interfaces.
	\item correct code instrumentation.
	\item handling of non-linear and non-convex optimization problems.
\end{enumerate}

Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions. The fourth aspect deals with code that relies on existing infrastructures and must be compliant with those, such as Linux kernel modules. The fifth aspect, in turn, is inherent to a large number of embedded systems from  telecommunications, control systems, and medical devices. In particular, software developed for that type of embedded systems has been extensively tested and verified, and also optimized for efficiency over years of development. Therefore, when a new product is derived from a given platform, a lot of legacy code is usually reused for improving development time and code quality. The sixth aspect is related to the evolution of development processes and technologies, which may delay the application of suitable verification and synthesis approaches, if verifiers and synthesizers do not support different programming languages and interfaces. The seventh aspect highlights a subjective task in verification: where one must insert an evaluation point or assertion, in order to correct address a property. Finally, the last one is related to the widespread use of embedded systems in autonomous-vehicle navigation systems~\cite{Adouane16}, which demands optimization solving during their execution for a wide range of functions, including non-linear and non-convex problems using fixed- and floating-point arithmetic.

Those eight challenges place additional difficulties for developing reliable synthesizers for embedded systems, especially for cyber-physical systems and micro-grids, where the controlled object ({\it e.g.}, physical plant) typically exhibits continuous behavior, whereas the controller (usually implemented by a real-time computer system) operates in discrete time and over a quantized domain. In particular, synthesizers for those systems need to consider the effects of quantizers (A/D and D/A converters), when a digital equivalent of the controlled object is considered, {\it i.e.}, a model of their physical environment (cf. intelligent product in Figure~\ref{intelligent-product}). Additionally,  finite-precision arithmetic and their related rounding errors need to be considered, when correct-by-construction code is generated for embedded systems.

>>>>

One may also notice that such a paradigm, {\it i.e.}, verification and synthesis based on an expected system behavior, is not restricted to digital filters and controllers or DMA races, but it can also be applied to possibly any real system, as long as the desired behavior can be expressed as properties in BMC frameworks. For instance, regarding self-driving cars, an important property could be the detection of pedestrians, animals, bicycles, or any obstacle present on urban and rural roads. Indeed, for instance, bicycles are considered one of the most difficult problems, due to the myriad of possible shape and colors \cite{selfcar}. In addition, the mentioned problem is closely related to machine learning, from which refinement strategies can be devised and incorporated to BMC approaches \cite{BMCml}.

@@

Generally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use some assertion-based verification and high-level processor models, during simulation~\cite{Behrend15,Lettnin09}, as shown in Figure~\ref{verification-methodologies}. 
%
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.35]{figure4.eps}
	\caption{Verification methodologies for embedded systems.}
	\label{verification-methodologies}
\end{figure}

In particular, the main challenges regarding verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, providing completeness, {\it i.e.},  if all possible states can be reached and evaluated, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness. Additionally, embedded system verification raises additional challenges, such as:
%
\begin{enumerate}
	\item Time and energy constraints;
	\item Handling of concurrent software;
	\item Platform restrictions;
	\item Verification of code pieces or modules that rely on larger structures;
	\item Legacy designs; %, which are usually developed with low-level languages.
	\item Support to different programming languages, frameworks, and interfaces;
	\item Correct code instrumentation;
	\item Handling of non-linear and non-convex optimization problems;
	\item Incorporation of new and adapted checks, due to system or environment evolution.
\end{enumerate}

Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions. The fourth aspect deals with code that relies on existing infrastructures and must be compliant with those, such as Linux kernel modules. The fifth aspect, in turn, is inherent to a large number of embedded systems from  telecommunications, control systems, and medical devices. In particular, software developed for that type of embedded systems has been extensively tested and verified, and also optimized for efficiency over years of development. Therefore, when a new product is derived from a given platform, a lot of legacy code is usually reused for improving development time and code quality. The sixth aspect is related to the evolution of development processes and technologies, which may delay the application of suitable verification and synthesis approaches, if verifiers and synthesizers do not support different programming languages and interfaces. The seventh aspect highlights a subjective task in verification: where one must insert an evaluation point or assertion, in order to correct address a property. The eighth one is related to the widespread use of embedded systems in autonomous-vehicle navigation systems~\cite{Adouane16}, which demands optimization solving during their execution for a wide range of functions, including non-linear and non-convex problems using fixed- and floating-point arithmetic. The ninth aspect is a consequence of changes in environment or different applications and scenarios, which may present new problems to embedded systems that did not exist or were not tackled during their development. Such a challenge is also closely related to ML techniques, given that they may be integrated into commercial systems and have the potential to devise new and refined control strategies, which must then be identified, checked, and validated. For instance, a diagnostic system may employ techniques that make it able to learn new tumor patterns and them warn their presence on patients' bodies, but a wrong updated model may compromise earlier traditional assessments and erroneously perform new ones, which should be verified and validated. Finally, the latter also raises another question: an embedded system must be checked only when it is developed/created or also during its life cycle, in order to ensure that improved models and actions are sound and reliable? That is an issue that will probably concern researchers, when ML becomes mature and widely spread.

Those nine challenges place additional difficulties for developing reliable synthesizers for embedded systems, especially for cyber-physical systems and micro-grids, where the controlled object ({\it e.g.}, physical plant) typically exhibits continuous behavior (which may eventually change), whereas the controller (usually implemented by a real-time computer system) operates in discrete time and over a quantized domain. In particular, synthesizers for those systems need to consider the effects of quantizers (A/D and D/A converters), when a digital equivalent of the controlled object is considered, {\it i.e.}, a model of their physical environment (cf. intelligent product in Figure~\ref{intelligent-product}). Additionally,  finite-precision arithmetic and their related rounding errors need to be considered, when correct-by-construction code is generated for embedded systems.
